### 2023-09-22 sections/projects.tex
Update projects.tex
LPPL v1.3c

\begin{cvhonors}
\cvhonor
{Chilean Political Science Impact Ranking} 
{This research have not received any specific grant. {\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/C8PRA}{\textcolor{blue}{10.17605/OSF.IO/C8PRA}}} 
{Coordinator}
{2020}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{COVID-19 Pandemic in South America}
{This research have not received any specific grant. {\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/6FM7X}{\textcolor{blue}{10.17605/OSF.IO/6FM7X}}}
{Coordinator}
{2020}
\end{cvhonors}

>>>>

\begin{cvhonors}
\cvhonor
{Chilean Political Science Impact Ranking} 
{This research has not received any specific grant. {\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/C8PRA}{\textcolor{blue}{10.17605/OSF.IO/C8PRA}}} 
{Coordinator}
{2020}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{COVID-19 Pandemic in South America}
{This research has not received any specific grant. {\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/6FM7X}{\textcolor{blue}{10.17605/OSF.IO/6FM7X}}}
{Coordinator}
{2020}
\end{cvhonors}
